Compare Austria with the world

```{r setup, include = FALSE}
library(tidyverse)
library(tidyverse)
library(coronavirus)
library(kableExtra)
library(base)
library(coronavirus)
library(tibble)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(tidyr)
library(plotly)
```

```{r, echo=FALSE, include=TRUE}
conf_df <- coronavirus %>% 
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(-total_cases) %>%
  mutate(parents = "Confirmed") %>%
  ungroup() 
  
  plot_ly(data = conf_df,
          type="sunburst",
          values = ~total_cases,
          labels= ~ country,
          parents=  ~parents,
          domain = list(column=0),
          name = "Confirmed",
          textinfo="label+value+percent parent")
```

The number of confirmed cases in Austria is very low, and the world ranks outside one hundred, which means it is almost invisible in the statistical graph.

Indicating that the number of infections in Austria is very low

```{r,echo=FALSE, include=TRUE}
conf_df <- coronavirus %>% 
  filter(type == "death") %>%
  group_by(country) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(-total_cases) %>%
  mutate(parents = "Death") %>%
  ungroup() 
  
  plot_ly(data = conf_df,
          type="treemap",
          values = ~total_cases,
          labels= ~ country,
          parents=  ~parents,
          domain = list(column=0),
          name = "Confirmed",
          textinfo="label+value+percent parent")
```

Although the number of infected people is not large, the mortality rate is about 65th in the world so we can see it in the graph.

Indicating that the cure rate is not high
